Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Updates

To enable researchers to easily apply our approach to their own datasets, we
also developed an interactive web-based tool (shown in Fig.~\ref{fig:web}) for
constructing models. Users can upload their dataset, which initializes an empty
DAG with nodes corresponding to the dataset's variables. They can then specify
a p-value threshold and a measure of association threshold. To make the method
work for mixed data types, we use a measure based on canonical correlations
(Appendix~\ref{sec:mixed_association}).

Using the specified thresholds, the tool visually highlights variable pairs
(using red edges) with a residual association higher than the threshold. The
thickness of these edges represents the strength of association, helping users
prioritize which variable pairs to address first. Similarly, if an edge in the
graph is detected to be unnecessary, it is highlighted in black. Based on this
information, make modifications to the model by adding or removing edges. The
tool also provides the Room Mean Square Error of Approximation (RMSEA) of the
overall model fit to the data. Once satisfied with the constructed DAG, users
can export the model for further analysis.

>>>>

To enable researchers to easily apply our approach to their own datasets, we
developed an interactive web-based tool (Figure~\ref{fig:web}) for constructing
DAGs. Users can upload their dataset, which initializes an empty DAG with nodes
corresponding to the dataset's variables. They can then specify a p-value
threshold and a measure of association threshold. To accommodate mixed data
types, we use a measure of association based on canonical correlations
(detailed in Appendix~\ref{sec:mixed_association}).

Using the specified thresholds, the tool visually highlights variable pairs
with a residual association greater than the threshold, marking them with red
edges. The thickness of these edges represents the strength of association,
helping users prioritize which variable pairs to address first. Similarly, if
an existing edge is superfluous, it is highlighted in black, signaling
potentially unnecessary edge. Using this information, users can iteratively
modify the model by adding or removing edges. The tool also computes the Root
Mean Square Error of Approximation (RMSEA) to provide an estimate of the
overall fit of the model. Once satisfied with the constructed DAG, users can
export the model for further analysis.
